Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-01-11 analysis/paper_draft3.Rmd
revision of paragraph on Cochran-Mantel-Haenszel test

Relying on historical strike data, however, requires an approach to missingness in the historical data or to the possibility that attorney's strike bias depends on certain trial-level characteristics that vary across trials (e.g., defendant race, charge severity). As a result, there may be incompatibility between plausible values of any attorney's bias parameter based on strike data for an attorney in the current trial and based on historical strike data for that attorney. Simply pooling the the strike data from current and past trials, and analyzing such data together, ignores such incompatibility, which can lead to inflated type I error and reduced power [@Bennett2020].

>>>>

Relying on historical strike data, however, requires an approach to missingness in the historical data or to the possibility that attorney's strike bias depends on certain trial-level characteristics that vary across trials (e.g., defendant race, charge severity). As a result, there may be incompatibility between plausible values of any attorney's bias parameter based on strike data for an attorney in the current trial and based on historical strike data for that attorney.

Simply pooling the the strike data from current and past trials, and analyzing such data together, ignores such incompatibility, which can lead to inflated type I error and reduced power [@Bennett2020]. To increase power, one may use other methods, such as stratifying strike data by trial and applying the Cochran-Mantel-Haenszel (CMH) test [@Gastwirth2014, 295-297]. Such approaches, however, do not directly address incompatibility between current and historical strike data. For example, applying the CMH test requires first selecting only historical strike data from past trials that are "similar" to the current trial [@Gastwirth2014, 289, 297]. Assessing such similarity implies weighting the available historical strike data with respect to some attorney-bias-related set of trial-level characteristics that are present or absent in the current trial.
